Title

### 2014-07-22 paper.tex
Working on Introduction section

\section{Introduction}
Motivation Example.\thai{Wow}
\begin{description}
\item[RQ1:] Can we identify useful and useless discussions in code review?
\item[RQ2:] How impact of useless discussion impact to the software quality?
\end{description}

@@

%\bibliography{references}

>>>>

\section{Introduction}
Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project. This method mainly intend to early identify defect before integrating changes. The formal inspection\cite{Fagan:1976:DCI:1661010.1661012} is a traditional technique for code review with well-defined structure.
However, with cumbersome process mandating a well-preparation and in-person meetings of formal inspection, Modern Code Review (MCR)\cite{Bacchelli2013a}, tool-based code reviews have received much attention nowadays and  put into software development regularly in both industrial and OSS projects. A major difference between MCR and inspection is the in-person meeting is not required in MCR. Reviewers can discuss to find defects through comments on code review tool. Then, developers will fix their changes following those comments.

As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998} \pick{and other papers}and MCR\cite{Mcintosh,Beller,Rigby,Hamasaki2013,Baysal2001}. This would in

%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

%Motivation Example.\thai{Wow}
%\begin{description}
%\item[RQ1:] Can we identify useful and useless discussions in code review?
%\item[RQ2:] How impact of useless discussion impact to the software quality?
%\end{description}

@@

\bibliography{references}
